\section{Conclusion}

\subsection{Main Conclusions and Hypothesis Evaluation}
This research set out to critically assess the comparative accuracy of vision-based and GPS-based speed estimation algorithms for autonomous vehicles. The primary research question asked how much a vision-based model, utilising Region of Interest (ROI) Dense Optical Flow and dynamic affine calibration, varies in accuracy compared to standard GPS probe data when evaluated against a high-quality CAN-bus ground truth. 

The main conclusion drawn from this experimental evaluation is definitive: consumer-grade GPS trajectory data significantly outperforms the proposed pure pixel-tracking vision methodology in both accuracy and stability. The GPS pipeline achieved a highly precise Mean Absolute Error (MAE) of 1.68 km/h, whereas the vision-based system trailed considerably with an MAE of 4.50 km/h—making the optical flow approach nearly three times less accurate. 

Consequently, these findings thoroughly address and overturn the original research hypothesis. The alternative hypothesis, which posited that the vision-based method would yield a smaller error margin than GPS during normal driving due to satellite latency and noise, is wholly rejected. Instead, the data proves that while GPS does exhibit a minor negative bias (-1.43 km/h) indicative of slight spatial lag, its overall capacity to capture the full dynamic range of a vehicle's kinematics in standard urban environments is markedly superior to Dense Optical Flow.

\subsection{Shortcomings in the Methodology}
While the experimental setup benefited from the highly synchronised, objective ground truth provided by the \textit{comma2k19} dataset, a critical evaluation of the research identifies several significant shortcomings inherent to the chosen methodology:

\begin{itemize}
    \item \textbf{Algorithmic Fragility and Lack of Semantic Understanding:} The primary methodological flaw lies in the reliance on the Farnebäck Dense Optical Flow algorithm. By calculating frame-by-frame pixel intensity displacements, the system tracks raw visual shifts rather than physical objects. The methodology failed to account for the fact that environmental visual noise—such as shadows cast by bridges, the relative motion of oncoming traffic, and the high-speed blurring of lane markings—artificially elevates pixel magnitude. This lack of semantic understanding led to a severe `flattening' effect where the algorithm completely failed to detect vehicle deceleration, resulting in a systemic overestimation of speed.
    \item \textbf{Limitations in Generalisability:} The experimental evaluation was fundamentally limited by its cross-sectional dataset constraints. The tested segment was recorded in well-lit, clear Californian weather conditions. Given that the optical flow methodology exhibited extreme volatility and broke down during minor lighting shifts (such as passing shadows) in ideal weather, its performance in adverse conditions (e.g., heavy rain, snow, or night-time driving) would be catastrophically degraded. Thus, the vision methodology lacks real-world transferability.
    \item \textbf{Camera Calibration Assumptions:} While the dynamic affine calibration continuously scaled the forward motion proxy using a rolling CAN-bus window, this method mathematically assumes a relatively stable camera pitch. In real-world scenarios, severe vehicle braking causes suspension dive (altering the camera's pitch), which physically shifts the vanishing point and corrupts the optical flow vectors. The current methodology did not integrate pitch-compensation algorithms to account for this physical variable.
\end{itemize}

\subsection{Suggestions for Further Research}
Based on the identified shortcomings and the comparative analysis of the data, several highly promising avenues for further research emerge to advance the field of Intelligent Transportation Systems (ITS):

\begin{enumerate}
    \item \textbf{Transition to Deep Learning (YOLO) Frameworks:} Future research attempting vision-based speed estimation should abandon pure pixel-displacement mathematics. Instead, studies should implement deep learning paradigms, such as YOLOv8 or YOLO11 object detection frameworks. By training a model to draw bounding boxes around specific vehicle classes, the system gains semantic comprehension. It can track the changing physical dimensions of a leading vehicle, entirely ignoring the peripheral visual noise, shadows, and lane markings that critically compromised the optical flow methodology in this study.
    \item \textbf{Implementation of Sensor Fusion via Kalman Filtering:} This study evaluated GPS and Vision as mutually exclusive, competing technologies. However, the data reveals that their strengths and weaknesses are perfectly complementary: GPS provides highly stable, weather-resistant positioning but suffers from slight latency, whilst camera data offers instantaneous kinematic responsiveness but is environmentally fragile. Further research should focus on developing a Sensor Fusion prototype. By employing a Kalman Filter to continuously merge both data streams—using GPS to anchor the steady-state speed and visual data to bridge the instantaneous latency gaps—a hybrid system could theoretically achieve sub-1 km/h error margins.
    \item \textbf{Algorithmic Noise Mitigation for GPS:} Given that the raw, uninstrumented GPS probe data performed exceptionally well, future research should explore applying Deep Neural Networks (DNNs) to standard satellite trajectories. Training a DNN to predict and smooth over multipath signal reflections in severe urban canyons could push affordable, consumer-grade GPS receivers to near-RTK levels of accuracy without the need for expensive hardware upgrades.
\end{enumerate}